---
title: "marshal_example"
output: html_document
date: "2023-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

**MARSHAL**, stand for MAize Root System Hydraulic Architecture soLver. It combines the root architecture model  CRootBox [@CrootBox] with the method for solving water flow in root system hydraulic architecture (RSHA) of Meunier et al. [-@Meunier2017-ue] with the method for computing macroscopic parameter of Couvreur et al. [-@Couvreur2012]. MARSHAL calculates root system conductance, 1 to 3-D uptake distribution and other upscaled variables (plant leaf water potential or transpiration) for any combination of structural and functional traits.

## How to use MARSHAL in the R environment

To run this example, the marshal package is required. This package can be found on [GitHub](https://github.com/MARSHAL-ROOT/marshal).
Alternatively, by simply executing the following line in the R environment:


```{r load_libraries}
########################################################################
# 1 : LOAD THE LIBRARIES AND SOURCE FILES
########################################################################

#library(tidyverse)
library(ggplot2)
library(plyr)
library(readr)
library(data.table)
library(dplyr)
library(Matrix)

# Custom functions
source("inputs/io_function.R") # CROOTBOX
source("inputs/getSUF.R") # MARSHAL
```



# Boundary conditions of MARSHAL.

The inputs of MARSHAL are:

- The hydraulic properties of the roots.
- The water potential of the soil.
- The root system architecture (RSA).
- The initial pressure strength that pulls water out of the collar.

We first start to load the hydraulic parameters, from the rootn the soil and the atmosphere

```{r load_hydro_params}
# MARSHAL PARAMETERS

# E. We load the default parameter sets for the simulation 
psiCollar <- -15000
soil <- read_csv("inputs/soil.csv")
conductivities <- read_csv("inputs/conductivities.csv")
```

Then we load the root system, that was generated using CPlantBox [[here](https://github.com/water-fluxes/day-3-plant-scale-cplantbox)]. We plot the root system to see what it looks like. 

```{r load_root}
# Root system

rootsystem <- fread("outputs/first_example.txt", header = T)

rootsystem %>%
  ggplot() +
  theme_classic() +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2), alpha=0.9) +
  coord_fixed()
```


We now have all the information we need to run the MARSHAL code in itself (one command). 

```{r compute_hydro}
########################################################################
# 4 : RUN MARSHAL
########################################################################
      
# Run MARSHAL
hydraulics <- getSUF(rootsystem, conductivities, soil, psiCollar)
```

Then we can get all the parameters of interest and add them to the root system information generated with CPlantBox

```{r cars}
hydraulic_archi <- hydraulics$root_system
hydraulic_archi$suf <- hydraulics$suf[,1]
hydraulic_archi$kr <- hydraulics$kr[,1]
hydraulic_archi$kx <- hydraulics$kx[,1]
hydraulic_archi$jr <- hydraulics$jr[,1]
hydraulic_archi$jxl <- hydraulics$jxl[,1]
hydraulic_archi$psi <- hydraulics$psi[,1]


print(paste0("KRS = ",hydraulics$krs))
print(paste0("Potential transpiration = ",hydraulics$tpot))
print(paste0("Actual transpiration = ",hydraulics$tact))
```
And we use this information to visuale the hydraulic properties of the root system, either in a detailled way : 

```{r plot_archi}
hydraulic_archi %>%
  ggplot() +
  theme_classic() +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, col = psi), alpha=0.9) +
  scale_color_viridis_c() + 
  coord_fixed()
```
